Proposed Solution

### 2016-11-14 Ennan-Proposal/travis.tex
stuff

TravisCI misconfigurations are important to detect and correct 
because of any failed compilation can costs developer significant amount 
of time. A misconfiguration can cause a test suite to run up to 20 
minutes, only to report a misconfiguration~\cite{API}.
The developer will need to wait to get such a report back to begin even identifying the error.

@@

Version space learning builds a logical constraint model for binary
classification~\cite{mitchell77}, which we use to test a configuration file for membership
in the set of all correct files.

We extend the \app's functionality to first learn the rules that have 
to hold for correct TravisCI configuration files. Traditionally, 
version space 
learning builds a model that defines membership using a series of 
disjunctions from a set of predefined hypotheses.  However, we need  to 
use conjunctions to convey that a configuration file is only correct if 
it satisfies all the learned relations. Those rules can be seen as
positive examples in classifying correct files. In addition, we will have
so-called {\emph {breaking rules}} which are derived from the files 
that do not compile, \ie negative examples. Breaking rules are specified 
using disjunctions.

\begin{figure}[!tbh]
  \centering
  \begin{tikzpicture}
    \draw (2,0) rectangle (6,2); \draw (2.5,0.5) rectangle (5.5,1.5);
  \end{tikzpicture}
  \caption{System architecture of }
  \label{fig:screenshot1}
\end{figure}

>>>>

TravisCI misconfigurations are important to detect and correct before execution,
because any failed compilation can costs developer significant amount 
of time. A misconfiguration can cause a test suite to run up to 20 
minutes, only to report that the whole computation failed~\cite{API}.
If developer would have this information prior to the compilation attempt, they could
 identifying and correct potential misconfigurations.

@@

We plan to use version space learning and SMT solvers to detect errors in 
TravisCI configurations files. Version space learning 
builds a logical constraint model for binary
classification~\cite{mitchell77}, which we use to test a configuration file for 
membership in the set of all correct files.

Figure~\ref{fig:versionSL} outlines our proposed approach. We first apply the standard \app's approach to learn the rules that have 
to hold for correct TravisCI configuration files. Traditionally, 
version space learning builds a model that defines membership using a series of 
disjunctions from a set of predefined hypotheses.  However, we need  to 
use conjunctions to convey that a configuration file is only correct if 
it satisfies all the learned relations. Those rules can be seen as
positive examples in classifying correct files. In addition, we will have
so-called {\emph {breaking rules}} which are derived from the files 
that do not compile, \ie negative examples. Breaking rules are specified 
using disjunctions.

\begin{figure}[!tbh]
  \centering
  \begin{tikzpicture}
   \draw[help lines]
    \draw (2,0) rectangle (6,2); \draw (2.5,0.5) rectangle (5.5,1.5);
  \end{tikzpicture}
  \caption{System architecture of }
  \label{fig:versionSL}
\end{figure}

Necessary = 
 { Keyword, value pair "language:node_js" requires Keyword "node_js"}

where keyword "node_js" sets a version value (e.g. "node_js: 0.8")

Breaking =
  { Keyword "node_js" cannot have value <= 0 }
